Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization

### 2019-05-13 presentation/paperv2.tex
added table

\subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
\noindent
For this problem the large feature size relative to the the number of labels dicitates looking
at Bayesian approach or some from of L1 regularization (HW1 problem 2) to push a large number
of coefficients to zero.
\begin{itemize}

\item Naive Bayes
\begin{equation*}
P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)
\end{equation*}

\item Logistic Lasso
\begin{equation*}
A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1
\end{equation*}

\end{itemize}

>>>>

\subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
\noindent
For this problem the large feature size relative to the the number of labels dicitates looking
at Bayesian approach or some from of L1 regularization (HW1 problem 2) to push a large number
of coefficients to zero.
\begin{itemize}
\item Naive Bayes
\begin{equation*}
P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)
\end{equation*}

\item Logistic Lasso
\begin{equation*}
A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1
\end{equation*}
\end{itemize}

\noindent 
For \textbf{Logistic Lasso} we are interested in examining the impact of the regularization parameter on
the fraction of  non-zero coefficients remaining after regularization is applied and on the impact of the predictive
score on test data. \\

\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
 \hline
 \multicolumn{6}{|c|}{Comparision of Logistic Lasso with different regularization} \\
 \hline
 \multicolumn{1}{|c|}{} &
 \multicolumn{1}{|c|}{} &
 \multicolumn{2}{|c|}{Unstacked} &
 \multicolumn{2}{|c|}{Stacked}\\
 \hline
 N-gram & $\alpha$ & F1 & frac remain & F1 & frac remain\\
 \hline

10:15 &  3.333 & 0.454 & 0.000040 & 0.720 & 0.000016 \\
10:15 &  2.000 & 0.575 & 0.000066 & 0.897 & 0.000029 \\
10:15 &  1.000 & 0.647 & 0.000148 & 0.893 & 0.000055 \\
10:15 &  0.500 & 0.679 & 0.000291 & 0.913 & 0.000094 \\
10:15 &  0.200 & 0.708 & 0.000339 & 0.913 & 0.000134 \\
10:15 &  0.100 & 0.710 & 0.000463 & 0.923 & 0.000161 \\
10:15 &  0.050 & 0.711 & 0.000619 & 0.925 & 0.000206 \\
10:15 &  0.020 & 0.715 & 0.000764 & 0.923 & 0.000243 \\
10:15 &  0.010 & 0.713 & 0.001045 & 0.913 & 0.000315 \\
10:15 &  0.002 & 0.730 & 0.001659 & 0.906 & 0.000517 \\
10:15 &  0.000 & 0.669 & 0.978049 & 0.669 & 1.000000 \\
 \hline
\end{tabular}
